Local PCA results

### 2016-05-13 medicago/summarize_run.Rmd
corner pcas added to summarize_run

Now, we'll look at PCA plots from the extracted corners.
```{r corner_pca, cache=TRUE}
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
                regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- do.call( rbind, tapply( 1:nrow(reg), reg$chrom, function (k) {
                        chrom <- reg$chrom[k[1]]
                        vcf_query( bcf.files[chrom], reg[k,] )
                }, simplify=FALSE ) )
            cov_pca(geno,k=4)
    } )
```

>>>>

Now, we'll look at PCA plots from the extracted corners.
(warning: takes awhile and a lot of RAM)
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
            regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- vcf_multi_query( chrom.list=chroms, file=bcf.files, regions=reg )
            cov_pca(geno,k=corner.npc)
    } )
```

First, here are the first `r corner.npc` PCs for each corner, together:
```{r plot_corner_pca, fig.width=3*fig.dim}
for (k in seq_along(mds.corners)) {
    vectors <- matrix( corner.pca[[k]][-(1:(1+corner.npc))], ncol=corner.npc )
    colnames(vectors) <- paste("PC", 1:corner.npc)
    pairs(vectors)
}
```
